%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.

%
% Creator Peilin Li
% Contact me via twitter/wechat: @pe1l1nl1
% linkedin.com/peill and/or github/ppeill
% Inspired by Peppa Pig
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\usepackage[left=0.40in,top=0.3in,right=0.75in,bottom=0.1in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \begin{center}

% \end{center}
\name{Lydia Csaszar} % Your name


%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\faGithub{\href{github.com/lcsaszar01}{github.com/lcsaszar01}} \faLink{\href{linkedin.com/in/lcsaszar01}{linkedin.com/in/lcsaszar01}}
\faEnvelope{\href{mailto:lcsaszar01@saintmarys.edu}{lcsaszar01@saintmarys.edu}}}
\address{\faMapMarker{ 58393 Crossview Lane Osceola, Indiana 46561} \faPhone(574) 855-6807} % Your address

\begin{document}
%%{\centerline {\em \textbf { Peppa pig wants a new job, job position from 20xx.01-20xx.01(delete it if needed) } } }


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}


{\bf Saint Mary’s College Information Technology | Notre Dame, IN} \hfill {\em August 2021 - Present}
\\{\textit{ResNet Consultant Student Manager}}
\\ - Coordinate communication between ResNet, Helpdesk, and Cluster Consultants.
\\ - Arranged moral booting group activities.
\\ - Fulfilled all the duties required of a ResNet Consultant.
%\\ - Listened to concerns of fellow consultants and worked to provide sustainable solutions to those concerns.

{\bf Saint Mary’s College Information Technology | Notre Dame, IN} \hfill {\em August 2019 - May 2021}
\\{\textit{ResNet Consultant}}
\\ - Enforced college security and fair use policies by configuring student's devices to meet college guidelines
\\ - Cleaned infected computers to improve performance on multiple student computers of different OS platforms.
\\ - Beta tested new college software to support virtual assistance.


{\bf Mursix | Yorktown, IN} \hfill {\em June 2021 - August 2021}
\\{\textit{Intern}}
\\ - 1 of 30 individuals selected out of 700+  for the TechPoint Xtern program
%\\ - Consulted on the special projects team concentrating on projects from small business contracts.
\\ - Conducted database cleanup reducing memory utilized database by 25\%
%\\ - Completed cleanup in 3 months when projected completion would take 6 months
\\ - Completed 20 computer enhancements, rebuilding existing computers and boosted computer hardware efficiency by removing out of date hardware under supply chain stress. Saving the company thousands of dollars through the reuse of good hardware and use of off the shelf parts.
\\ - Designed and 3D printed a working prototyped a tool using CAD that reduced hand assembly time from 3 minutes to 20 seconds and could be added to automation and further at scale improvements
\\ - Engaged in community outreach by assisting with an IoT camp and hosted a talk with the Nappanee robotics club about STEM majors/career paths
%\\ - Explored the tech industry though TedTalk-style sessions to expand my knowledge base by learning from industry professionals

{\bf University of Notre Dame Data Structures Preternship |  Notre Dame, IN} \hfill {\em February 2021 - May 2021}
\\{\textit{Software Engineer}}
\\ - Developed a Proof of Concept scheduler to organize and graph the data of small scale data sets. Utilizing the AWS environment, we improving automated analysis of small data sets by 10\%.

{\bf Saint Mary’s College Information Technology | Notre Dame, IN
} \hfill {\em May 2019 - May 2020}
\\{\textit{Helpdesk Consultant}}
\\ - Created detailed tickets about issues that faculty are experiencing so the proper tech can help.
%\\ - Answered the phone and replied to emails with troubleshooting solutions.
\\ - Assisted with delivery and set up of newly issued computers to professor
\\ - Assisted in the replacement of computer lab hardware and installation of new hardware and imaging by syncing with the imaging server. Improving the productivity of class time in the lab by 5\%.
%\\ - Unpacked and Organized computer hardware stockroom saving 3 hr+ of upper level IT staff time.

{\bf Saint Mary’s College Information Technology | Notre Dame, IN
} \hfill {\em September 2018 - May 2019}
\\{\textit{Cluster Consultant}}
\\ - Maintained printers by keeping paper stocked and loading fresh toner.
\\ - Kept work spaces clean by clearing trash and pushing in chairs.

{\bf Advanced Custom Homes and Remodeling | Osceola, IN} \hfill {\em September 2017 - May 2018}
\\{\textit{Administrative Intern}}
\\- Filed paid invoice paperwork so the company had a digital record for finances.
\\- Digitized record-keeping to reduce the space of the paper files in storage.

\newpage
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Notre Dame | Notre Dame, IN } \hfill {\em Expected Graduation December 2023}
\\{ \textit {Bachelors of Science, Dual Degree: Computer Engineering, }} \newline
\begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
Key Courses: {{ } }\begin{tabular}{@{} >{}l @{\hspace{1ex}} l}
     & \ Data Structures, \ Logic Design, \ Operating Systems, \ Systems Programming, \ Intro to EE
\end{tabular} \\
\end{tabular}


{\bf Saint Mary's College | Notre Dame, IN} \hfill {\em Expected Graduation May 2022}
\\ { \textit {Bachelor of Science, Dual Degree: Computing and Applied Mathematics}} \hfill
\begin{itemize}
    \item Academic/Merit-Based Awards: LeMan’s Scholarship (2018 - Present) and Tuohy Family Scholarship (2019 - Present)
\end{itemize}
\begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
Key Courses: {{ }\begin{tabular}{@{} >{}l @{\hspace{1ex}} l}
     & \ Discrete Mathematics, \ Databases, \ Probability \& Statistics, Systems Analysis \& Design
\end{tabular}} \\
\end{tabular}

%in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages: {{ }\begin{tabular}{@{} >{}l @{\hspace{6ex}} l}
     & \ R, Python, C/C++, SQL, CSS, HTML, MATLAB, (currently learning) Ruby on Rails
\end{tabular}} \\

%Programming: \ & aaa,bbb,ccc,ddd,eee,fff,ggg,hhh \\
Software \& Tools: %& {\textbf{Backend: }}qqqq,wwww,eeee,rrrr,tttt,yyyy,uuuu,iiii\\
{{ } \begin{tabular}{@{} >{}l @{\hspace{6ex}} l}
     & \\Proficient in Microsoft 365 and G Suite applications
     & \\ Trained in basic usage of Microsoft Azure and AWS business applications
\end{tabular}}
\end{tabular}

\end{rSection}

% \begin{rSection}{Carrier Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------


\begin{rSection}{Projects} %and Presentations}

{\bf IoT Smart Home Project} \hfill {\em Summer 2020 - Januanry 2021}
\\{\textit{Designer \& Project Coordinator}}
\\- Designed IOT enabled home taking into consideration building infrastructure, city codes, and client desired access points to wired connection.
\\ - Implemented server rack to manage all IOT within home
\\- Utilized EERO wifi5 mesh system to sync with Google Nest Secure Hub managing 25+ devices and home security utilities.
\\- Supervised and coordinated internet service provider and contractors to install network cabling

%{\bf Saint Mary’s College | Notre Dame, IN} \hfill {\em September 2021}
%\\{\textit{STEM Fall Poster Day - Internship Presentation}}
%\\- TechPoint Class of 2021 Experience - Muncie Division
%\\ - Presented on opportunities for STEM majors to work in the Indiana tech sector and discussed key policy shifts in Indiana's view of tech that will shape its 10 year job and economic growth vision.

%{\bf Saint Mary’s College | Notre Dame, IN} \hfill {\em September 2019}
%\\{\textit{STEM Fall Poster Day - Work Experience Presentation}}
%\\- A Summer at Saint Mary’s Helpdesk
%\\ - Presented on opportunities for students to gain IT experience and problem solving skills by working for the IT department. Highlighted how upcoming software would allow for remote connection help decreasing problem resolution turn around time by 15\%

\end{rSection}

%----------------------------------------------------------------------------------------
%	Extracurricular Section

%----------------------------------------------------------------------------------------
\begin{rSection}{CAMPUS LEADERSHIP AND INVOLVEMENT}


{\bf Society of Women Engineering | Saint Mary’s College
} \hfill {\em }
\\{\textit{Member | October 2019 - Present}}

{\bf Math Club | Saint Mary’s College} \hfill {\em}
\\{\textit{Vice President | Spring 2021 - Present}}
\\{\textit{Member | September 2020 - Present}}
\\ - Co-chaired on the design for the annual club shirt
\\ - Designed the annual door decorations

%{\bf Disney Club | Saint Mary’s College} \hfill {\em}
%\\{\textit{Member | Fall 2020 - Present}}

%{\bf Commuters Club | Saint Mary’s College
%} \hfill {\em}
%\\{\textit{Member | Fall 2020 - Present}}
%
\end{rSection}


%\begin{rSection}{Award}
%- First Prize\\
%- Second Prize\\
%- Third Prize\\
%\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------

\end{document}
